\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{enumitem}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE \scshape Tom Bleher} \\ \vspace{1pt}
    \href{mailto:tombleher@tauex.tau.ac.il}{tombleher@tauex.tau.ac.il} $|$ 
    {+972-50-676-2871} $|$
    \href{https://english.tau.ac.il/profile/tombleher}{Website}
\end{center}

%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tel Aviv University}{Tel Aviv, Israel}
      {Research Assistant}{May 2024 -- Present}
      \resumeItemListStart
        \resumeItem{}
          {Conducting simulations to evaluate particle detectors for the Electron-Ion Collider.}
      \resumeItemListEnd

    \resumeSubheading
      {Max Planck Institute for Plasma Physics}{Munich, Germany}
      {Research Assistant}{Sep 2024 -- Oct 2024}
      \resumeItemListStart
        \resumeItem{}
          {Developed internal simulation tools to assess next generationfusion reactor concepts.}
      \resumeItemListEnd

    \resumeSubheading
      {Max Planck Institute for Plasma Physics}{Greifswald, Germany}
      {Research Assistant}{Feb 2024 -- Apr 2024}
      \resumeItemListStart
        \resumeItem{}
          {Analyzed plasma profiles to examine impurity transport, contributed to an upcoming paper.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Institut national de la recherche scientifique}{Montreal, Canada}
      {Research Assistant}{Oct 2023 -- Jan 2024}
      \resumeItemListStart
        \resumeItem{}
          {Developed software to optimize x-ray flux from laser wakefield acceleration by correction of optical components.}
      \resumeItemListEnd

    \resumeSubheading
      {Tel Aviv University (with Stanford)}{Tel Aviv, Israel}
      {Research Assistant}{Aug 2023 -- Oct 2023}
      \resumeItemListStart
        \resumeItem{}
          {Prepared CAD models and directed preparation for direct laser acceleration experiments from heavy water microjet.}
      \resumeItemListEnd

    \resumeSubheading
      {Weizmann Institute of Science}{Rehovot, Israel}
      {Research Assistant}{Jul 2023}
      \resumeItemListStart
        \resumeItem{}
          {Analyzed experimental data to examine theoretical predictions on ultra-light dark matter behavior.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tel Aviv University}{Tel Aviv, Israel}
      {Bachelor of Science in Physics and Mathematics}{May 2024 -- Dec 2027}
      \resumeItemListStart
        \resumeItem{}
          {Coursework: Analysis I, Linear Algebra I, Expanded Intro to CS, Physics I, Set Theory, Physics Mathematical Methods I, Physics Lab I, British Culture I.}
      \resumeItemListEnd

    \resumeSubheading
      {Herzliya Hebrew Gymnasium}{Tel Aviv, Israel}
      {Physics, Mathematics, Computational Physics, Mechatronics}{Sep 2020 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{}
          {GPA: 93/100; SAT: 1490/1600 (Psychometric: 718/800)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart
      \resumeItemListStart
        \resumeItem{}
          {T. Romba, F. Reimold, S. Bannmann, A. Navarro, \textbf{T. Bleher}, et al. (2024). \href{https://pure.mpg.de/pubman/faces/ViewItemOverviewPage.jsp?itemId=item_3610374_1}{Characterizing scenarios of suppressed anomalous impurity transport in Wendelstein 7-X (Upcoming).}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- Awards \& Recognition-----------
\section{Awards \& Recognition}
  \resumeSubHeadingListStart
      \resumeItemListStart
        \resumeItem{}
          {Awarded full-ride scholarship and selected to represent Israel in the Dr. Bessie F. Lawrence International Summer Science Institute (ISSI) at the Weizmann Institute of Science.}
        \resumeItem{}
          {Placed 2nd in the Schwartz-Reisman poster competition for computational physics with \href{https://github.com/ilayws/SSoF}{"Spontaneous Synchronization of Fireflies"} and 3rd for \href{https://github.com/ilayws/NonuniformWaves}{"Wave Simulation in non-uniform Medium."}}          
          \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------LEADERSHIP & ACTIVITIES-----------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hapoel Beit Dani Wrestling Club}{Tel Aviv, Israel}
      {Wrestler, Team Captain}{Oct 2012 -- Present}
      \resumeItemListStart
        \resumeItem{}
          {Led a team of 30 wrestlers, competing nationally and internationally, and served as a past Israel national team member. Organized and motivated team activities and training sessions.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Middle East Entrepreneurs of Tomorrow}{Jerusalem, Israel}
      {Student, Teaching Assistant}{Sep 2019 -- Feb 2023}
      \resumeItemListStart
        \resumeItem{}
          {Instructed Python to high school students to enrich their existing curriculum.}
        \resumeItem{}
          {Facilitated learning by mentoring, hosting office hours, and creating team bonding activities, enhancing student engagement.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS & INTERESTS-----------

\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical Skills}{: Python, Linux, CAD, JavaScript, Git, LaTeX} \\
     \textbf{Foreign Languages}{: Hebrew (Native), English (Bilingual), Lithuanian (Proficient), Russian (Conversational)} \\
     \textbf{Interests}{: Guitar Playing, Vinyl Collecting, Classical Novels, History, Self-study}
    }}
 \end{itemize}
 
%-------------------------------------------
\end{document}